Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-06-27 paper/paper.Rmd
discuss setting `theRange` arg in blocking CV

>>>>

<!-- spcv_block: how to set argument `theRange` -->
Method `"spcv_block"` requires the user to supply a value for argument `theRange` which denotes the block size used to create the blocking scheme across the study area.
This specification is non-trivial and therefore package \pkg{blockCV} provides some helper functions (`spatialAutoRange()` and `rangeExplorer()`) to conduct a data-driven estimation of the distance at which the spatial autocorrelation in the data levels off [@blockCV].
According to the package authors, this estimate should then be used for argument `theRange` to have a sensible value for the block sizes created in method `"spcv_block"`.
